### 2025-07-11 factor-analysis.qmd
20250710 - fix plots

lavaanPlot::lavaanPlot(
  efa_fit$nf3,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa1factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa2factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

>>>>

lavaanPlot::lavaanPlot(
  efa_fit$nf3,
  coefs = TRUE,
  #covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factor_fit,
  coefs = TRUE,
  covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factorModified_fit,
  coefs = TRUE,
  #covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa1factor_fit,
  coefs = TRUE,
  #covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa2factor_fit,
  coefs = TRUE,
  covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factor_fit,
  coefs = TRUE,
  covs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factorModified_fit,
  coefs = TRUE,
  #covs = TRUE,
  stand = TRUE)
```
